\dirtree{%
    .1 /code.
    .2 CMakeLists.txt.
    .2 include.
    .3 CalculationOfAccelerationResistanceOfSecondaryCircuitWaterRisingSpace.h.
    .3 CalculationOfFrictionalResistanceInUTube.h.
    .3 CalculationOfLocalResistanceOfPrimaryCircuitWater.h.
    .3 CalculationOfResistanceOfFlowDistributionOrificeInSecondaryWaterRisingSpace.h.
    .3 CalculationOfResistanceOfSecondaryCircuitWaterVaporSeparator.h.
    .3 CalculationOfTheFrictionalResistanceOfTheSecondaryCircuitWaterRisingSpace.h.
    .3 CalculationOfTheLocalResistanceOfTheSecondaryCircuitWaterRisingSpace.h.
    .3 CalculationOfTheResistanceOfTheWaterBendInTheSecondaryCircuitWaterRiseSpace.h.
    .3 CalculationOfTheSpaceResistanceOfTheSecondaryCircuitWaterDrop.h.
    .3 CalculationOfTheTotalResistanceOfTheSecondaryCircuitWaterRisingSpace.h.
    .3 CalculationOfTotalResistanceOfPrimaryCircuitWater.h.
    .3 CalculationOfTotalResistanceOfSecondaryCircuitWaterCirculation.h.
    .3 GivenCondition.h.
    .3 HeatTransferCalculation.h.
    .3 HeatTransferTube.h.
    .3 LowerCylinder.h.
    .3 MainPipeInnerDiameter.h.
    .3 MotionHeadCalculation.h.
    .3 PreheatingSectionHeightCalculation.h.
    .3 SphericalBottomHead.h.
    .3 TubeBundleStructure.h.
    .3 UpperCylinder.h.
    .2 main.cpp.
    .2 src.
    .3 CalculationOfAccelerationResistanceOfSecondaryCircuitWaterRisingSpace.cpp.
    .3 CalculationOfFrictionalResistanceInUTube.cpp.
    .3 CalculationOfLocalResistanceOfPrimaryCircuitWater.cpp.
    .3 CalculationOfResistanceOfFlowDistributionOrificeInSecondaryWaterRisingSpace.cpp.
    .3 CalculationOfResistanceOfSecondaryCircuitWaterVaporSeparator.cpp.
    .3 CalculationOfTheFrictionalResistanceOfTheSecondaryCircuitWaterRisingSpace.cpp.
    .3 CalculationOfTheLocalResistanceOfTheSecondaryCircuitWaterRisingSpace.cpp.
    .3 CalculationOfTheResistanceOfTheWaterBendInTheSecondaryCircuitWaterRiseSpace.cpp.
    .3 CalculationOfTheSpaceResistanceOfTheSecondaryCircuitWaterDrop.cpp.
    .3 CalculationOfTheTotalResistanceOfTheSecondaryCircuitWaterRisingSpace.cpp.
    .3 CalculationOfTotalResistanceOfPrimaryCircuitWater.cpp.
    .3 CalculationOfTotalResistanceOfSecondaryCircuitWaterCirculation.cpp.
    .3 GivenCondition.cpp.
    .3 HeatTransferCalculation.cpp.
    .3 HeatTransferTube.cpp.
    .3 LowerCylinder.cpp.
    .3 MainPipeInnerDiameter.cpp.
    .3 MotionHeadCalculation.cpp.
    .3 PreheatingSectionHeightCalculation.cpp.
    .3 SphericalBottomHead.cpp.
    .3 TubeBundleStructure.cpp.
    .3 TubeSheet.cpp.
    .3 TubeSheet.h.
    .3 UpperCylinder.cpp.
}

\vspace{2cm}
程序已开源，代码详情见\href{https://github.com/iuming/SteamGeneratorDesign/tree/main/code}{Github}。